Can Auxiliary Indicators Improve COVID-19 Forecasting and Hotspot Prediction?

### 2021-10-31 forecast/paper/paper.tex
New paragraph in disc

As described previously, it is likely that we could improve the indicator models
by using location-specific effects, as well as using nowcasting techniques to
estimate finalized indicator values before we use them as features (to account
for backfill in the claims-based signals in particular).  Beyond this, it is
certainly possible that more sophisticated models for forecasting or hotspot
prediction would lead to different results, and possibly even different
insights. Natural directions to explore include using multiple indicators in a
single model, allowing for interaction terms, and leveraging HRR demographics or
mobility patterns.  That said, we are doubtful that more sophisticated modeling
techniques would change the ``topline'' conclusion---that auxiliary indicators
can provide nontrivial, consistent, but modest gains in forecasting and hotspot
prediction. Whether a more sophisticated model would be able to leverage the
indicators in such a way as to change some of the finer conclusions (e.g., by 
offering clear improvements in periods in which cases are trending up) is less 
clear to us.

>>>>

As described previously, it is likely that we could improve the indicator models
by using location-specific effects, as well as using nowcasting techniques to
estimate finalized indicator values before we use them as features (to account
for backfill in the claims-based signals in particular).  Beyond this, it is
certainly possible that more sophisticated models for forecasting or hotspot
prediction would lead to different results, and possibly even different
insights. Natural directions to explore include using multiple indicators in a
single model, allowing for interaction terms, and leveraging HRR demographics or
mobility patterns.  That said, we are doubtful that more sophisticated modeling
techniques would change the ``topline'' conclusion---that auxiliary indicators
can provide clear but modest gains in forecasting and hotspot prediction.

However, rigorously vetting the details for more sophisticated models, as well
as the generalizability of our findings to different geographic resolutions,
both remain important directions for future study.  For example, in the
Supplementary Materials we show that for forecasting at the state level, the
benefits provided by indicators models over AR are generally less clear
(compared to those observed at the HRR level).  One hypothesis is that at the
state level, where the signal-to-noise ratio (SNR) is higher, AR performs even
better and provides a higher standard (when asking whether it can be improved
upon using indicators).  At the HRR level, where the SNR is lower, including the
indicators as additional linear features in the AR model likely serves as an
important variance reduction (just like averaging independent terms would) which
contributes to improved accuracy.  But at a higher SNR, this variance
reduction becomes less important, and we may be compelled to use more
sophisticated modeling techniques to extract comparable value from the
indicators.
